\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/chaining.tex
s/Segal et al./Bandits/g

We found that our protocol was able to process, in the average case, 197.4 ciphertexts per second. To return to our example from earlier of a network with an average of 30 contacts per user, a lawful contact-chaining search with $k=2$ would have 900 users in the output, and a search with $k=3$ would have 27,000 users in the output. To compare these times to some of our acutal experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run. To provide another point of comparison, \cite{sff-foci2014} referred to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies. In one of our experiments with lawful contact chaining, we find that a similarly sized data set of 149,535 ciphertexts took 625.08 seconds - 10.4 minutes - to compile with our protocol. Given the context of a criminal investigation, we feel these running times are quite reasonable.

>>>>

We found that our protocol was able to process, in the average case, 197.4 ciphertexts per second. To return to our example from earlier of a network with an average of 30 contacts per user, a lawful contact-chaining search with $k=2$ would have 900 users in the output, and a search with $k=3$ would have 27,000 users in the output. To compare these times to some of our acutal experiments, we found that a search that returned 937 ciphertexts took 6.86 seconds to run, and a search that returned 27,338 ciphertexts took 109.55 seconds to run. To provide another point of comparison, Bandits~\cite{sff-foci2014} refers to the ``High Country Bandits'' case, in which the FBI performed an intersection of 150,000 phone number to help solve a series of bank robberies. In one of our experiments with lawful contact chaining, we find that a similarly sized data set of 149,535 ciphertexts took 625.08 seconds - 10.4 minutes - to compile with our protocol. Given the context of a criminal investigation, we feel these running times are quite reasonable.

### 2016-02-29 paper/conc.tex
s/Segal et al./Bandits/g

\section{Open Problems and Future Work}\label{sec-future}
Segal {\it et al.} noted in \cite[Section 6.1]{sff-foci2014} that
set intersection is but one type of computation that can be of use
to law-enforcement and intelligence agencies.  They observed that it 
would be interesting to identify other such computational problems 
and to devise accountable, privacy-preserving protocols to solve them.  
The work in this paper on contact chaining represents progress in that
direction.

>>>>

\section{Open Problems and Future Work}\label{sec-future}
Bandits noted in \cite[Section 6.1]{sff-foci2014} that
set intersection is but one type of computation that can be of use
to law-enforcement and intelligence agencies.  They observed that it 
would be interesting to identify other such computational problems 
and to devise accountable, privacy-preserving protocols to solve them.  
The work in this paper on contact chaining represents progress in that
direction.

### 2016-02-29 paper/intersection.tex
s/Segal et al./Bandits/g

Segal \emph{et al.}~\cite{sff-foci2014} presented a private set intersection
protocol, based on the ElGamal~\cite{elgamal} and Pohlig-Hellman~\cite{pohlighellman}
cryptosystems, to address these specific concerns. We present a summary of that protocol
in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
of users in the intersection of the sets under consideration, leaving the other,
untargeted users' identities hidden by encryption. To provide accountability and
oversight, the protocol requires multiple government agencies to participate. This
provides a division of authority. No one agency can uncover users' identities
without other agencies being able to collect records about how often intersection
warrants are used and set restrictions on how many users the agencies can identify
under a single warrant.

>>>>

Bandits~\cite{sff-foci2014} presented a private set intersection
protocol, based on the ElGamal~\cite{elgamal} and Pohlig-Hellman~\cite{pohlighellman}
cryptosystems, to address these specific concerns. We present a summary of that protocol
in Section~\ref{sec-isectproto}. This protocol reveals \emph{only} the identities
of users in the intersection of the sets under consideration, leaving the other,
untargeted users' identities hidden by encryption. To provide accountability and
oversight, the protocol requires multiple government agencies to participate. This
provides a division of authority. No one agency can uncover users' identities
without other agencies being able to collect records about how often intersection
warrants are used and set restrictions on how many users the agencies can identify
under a single warrant.

### 2016-02-29 paper/intro.tex
s/Segal et al./Bandits/g

Adopting the approach taken by Segal {\it et al.}~\cite{sff-foci2014}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

The utility of set-intersection protocols was demonstrated in the 
High Country Bandits case~\cite{anderson13cell}.
After obtaining cell-tower dumps -- sets of about 150,000 total users
whose cell phones had been in the vicinity of three banks at the times
that those banks were robbed -- the FBI intersected the sets and discovered 
that a single phone had been used at all of the relevant times in all of the 
relevant places.  They arrested the owner
of that phone and were able to prove that he was one of the robbers.
Although this FBI dragnet was effective in catching robbers, it also swept
in the cell-phone numbers of approximately 149,999 innocent bystanders.
Segal {\it et al.}~\cite{sff-foci2014} provide an accountable protocol for
set intersection that preserves the privacy of innocent bystanders.  Their
rudimentary implementation requires just under two hours on a test instance
with 150,000 total users.  In Section~\ref{sec-intersection} below, we provide
a more careful implementation that is faster by a factor of 10; in particular,
it runs for approximately 10.5 minutes on the test instance of 150,000 users.

>>>>

Adopting the approach taken by Bandits~\cite{sff-foci2014}\footnote{For the
purpose of anonymization, we present an anonymized version of this manuscript and
refer to the authors throughout as ``Bandits''.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

The utility of set-intersection protocols was demonstrated in the 
High Country Bandits case~\cite{anderson13cell}.
After obtaining cell-tower dumps -- sets of about 150,000 total users
whose cell phones had been in the vicinity of three banks at the times
that those banks were robbed -- the FBI intersected the sets and discovered 
that a single phone had been used at all of the relevant times in all of the 
relevant places.  They arrested the owner
of that phone and were able to prove that he was one of the robbers.
Although this FBI dragnet was effective in catching robbers, it also swept
in the cell-phone numbers of approximately 149,999 innocent bystanders.
Bandits~\cite{sff-foci2014} provide an accountable protocol for
set intersection that preserves the privacy of innocent bystanders.  Their
rudimentary implementation requires just under two hours on a test instance
with 150,000 total users.  In Section~\ref{sec-intersection} below, we provide
a more careful implementation that is faster by a factor of 10; in particular,
it runs for approximately 10.5 minutes on the test instance of 150,000 users.

### 2016-02-29 paper/open.tex
s/Segal et al./Bandits/g

\section{The Openness Principle in Lawful Surveillance}\label{sec-open}
In this section, we review the openness principle put forth by Segal 
{\it et al.}~\cite{sff-foci2014}.  Readers familiar with \cite{sff-foci2014} 
may skip to the next section.

@@

More precisely, Segal {\it et al.}~\cite{sff-foci2014} draw a distinction 
between two classes of communication-system users.  {\it Targeted users} are 
those who are under suspicion and are targets of properly authorized warrants.
All others are {\it untargeted users}; they are the vast majority of all 
users of a general-purpose, mass-communication system.  Segal {\it et 
al.}~\cite{sff-foci2014} posit that the
following {\it Openness Principle} should govern all surveillance activity
in a democratic society:
\begin{enumerate}
\item[I]
Any surveillance or law-enforcement process
that obtains or uses private information
about untargeted users shall be
an open, public, unclassified process.
\item[II]
Any secret surveillance or law-enforcement processes shall use only:
\begin{enumerate}
\item[(a)] public information, and
\item[(b)] private information about targeted users obtained under 
authorized warrants via open surveillance processes.
\end{enumerate}
\end{enumerate}
Segal {\it et al.} interpret this principle as a requirement that an open
``privacy firewall'' be placed between government agencies and citizens'
private information in a mass-communication network.  Processes that move
untargeted users' private information through the firewall must be open
processes.  The targeted class contains both {\it known} users, {\it i.e.},
those for whom the government has a name, address, phone number, email address,
or other piece of personally identifying information, and {\it unknown} users.
It is not, as it may seem on the surface, oxymoronic to call a user both
``targeted'' and ``unknown,'' because ambient information may justify the
targeting of an individual without identifying him or her in any standard sense
of ``identify.''  For example, a government agency may obtain a ``John Doe
warrant''~\cite{bieber-penn2002} to investigate users who were present in
locations $L_i$ at times $T_i$, for $1\leq i\leq k$, without being able to 
identify those users, because relevant events occurred at those locations at
those times. Segal {\it et al.}~\cite{sff-foci2014} show how an 
accountable-surveillance protocol can be used to obtain a large set of
{\it encrypted} data about both targeted and untargeted users, feed it into a 
cryptographic protocol that winnows it down to the records of users targeted by
the John Doe warrant, and decrypt {\it only} those records.  Thus, targeted
unknown users can be identified ({\it i.e.}, turned into targeted, known users)
without government agencies' identifying any untargeted users whose 
encrypted records are touched by the surveillance process.

>>>>

\section{The Openness Principle in Lawful Surveillance}\label{sec-open}
In this section, we review the openness principle put forth by
Bandits~\cite{sff-foci2014}.  Readers familiar with \cite{sff-foci2014} 
may skip to the next section.

@@

More precisely, Bandits~\cite{sff-foci2014} draw a distinction 
between two classes of communication-system users.  {\it Targeted users} are 
those who are under suspicion and are targets of properly authorized warrants.
All others are {\it untargeted users}; they are the vast majority of all 
users of a general-purpose, mass-communication system. Bandits~\cite{sff-foci2014}
posit that the following {\it Openness Principle} should govern all surveillance
activity in a democratic society:
\begin{enumerate}
\item[I]
Any surveillance or law-enforcement process
that obtains or uses private information
about untargeted users shall be
an open, public, unclassified process.
\item[II]
Any secret surveillance or law-enforcement processes shall use only:
\begin{enumerate}
\item[(a)] public information, and
\item[(b)] private information about targeted users obtained under 
authorized warrants via open surveillance processes.
\end{enumerate}
\end{enumerate}
Bandits interpret this principle as a requirement that an open
``privacy firewall'' be placed between government agencies and citizens'
private information in a mass-communication network.  Processes that move
untargeted users' private information through the firewall must be open
processes.  The targeted class contains both {\it known} users, {\it i.e.},
those for whom the government has a name, address, phone number, email address,
or other piece of personally identifying information, and {\it unknown} users.
It is not, as it may seem on the surface, oxymoronic to call a user both
``targeted'' and ``unknown,'' because ambient information may justify the
targeting of an individual without identifying him or her in any standard sense
of ``identify.''  For example, a government agency may obtain a ``John Doe
warrant''~\cite{bieber-penn2002} to investigate users who were present in
locations $L_i$ at times $T_i$, for $1\leq i\leq k$, without being able to 
identify those users, because relevant events occurred at those locations at
those times. Bandits~\cite{sff-foci2014} show how an 
accountable-surveillance protocol can be used to obtain a large set of
{\it encrypted} data about both targeted and untargeted users, feed it into a 
cryptographic protocol that winnows it down to the records of users targeted by
the John Doe warrant, and decrypt {\it only} those records.  Thus, targeted
unknown users can be identified ({\it i.e.}, turned into targeted, known users)
without government agencies' identifying any untargeted users whose 
encrypted records are touched by the surveillance process.

### 2016-02-29 paper/related.tex
s/Segal et al./Bandits/g

Kamara~\cite{kamara}
and Kroll {\it et al.}~\cite{kroll} used cryptographic protocols to 
achieve privacy and accountability in the surveillance of known targets.
Segal {\it et al.}~\cite{sff-foci2014} formulated the openness principle that
we have followed and were the first to design privacy-preserving protocols for
the surveillance of unknown targets.

>>>>

Kamara~\cite{kamara}
and Kroll {\it et al.}~\cite{kroll} used cryptographic protocols to 
achieve privacy and accountability in the surveillance of known targets.
Bandits~\cite{sff-foci2014} formulated the openness principle that
we have followed and were the first to design privacy-preserving protocols for
the surveillance of unknown targets.

### 2016-02-29 paper/submission.tex
s/Segal et al./Bandits/g

\begin{thebibliography}{99}
%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e= 
%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
Open Communications on the Internet, August 18, 2014, San Diego, 
USA (USENIX, Berkeley, 2014)

>>>>

\begin{thebibliography}{99}
%\bibitem{journal-1} A.~P.~Raposo, H.~J.~Weber, D.~E.~Alvarez--Castillo, M.~Kirchbach, Cent. Eur. J. Phys. 5, 253 (2007)
%\bibitem{journal-2} J.~Barth et al. (SAPHIR Collaboration), Phys. Lett. B 572, 127 (2003)
%\bibitem{journal-3} S.~Chekanov et al., Eur. Phys. J. C 51, 289 (2007)
%\bibitem{journal-4} K.~Malarz, Postepy Fizyki 57, 235 (2006) (in Polish)
%\bibitem{journal-5} G.~Meng, Cent. Eur. J. Phys., DOI:10.2478/s11534-007-0038-1
%\bibitem{journal-6} R.~Hegselmann, U.~Krause, Journal of Artificial Societies and Social Simulation (2006), https://urldefense.proofpoint.com/v2/url?u=http-3A__jasss.soc.surrey.ac.uk_9_3_10.html&d=AwIGaQ&c=-dg2m7zWuuDZ0MUcV7Sdqw&r=TO0xacJWWmvm7m0roFn_liAsIL2PkxELeLGL8JNJXFw&m=Ka2FvolwqKNW8vu0FjJrZZz-0NBFnF_Zu-dQp-fjTto&s=370GY1pBTDyr9NSQToGqkNR8K-Xy1z0bsX64GpcLiPk&e= 
%\bibitem{journal-7} A.~Dybala, Cent. Eur. J. Chem. (in press)
%\bibitem{journal-8} A.~Dybala, Przeglad chemiczny (in Polish, in press)
%\bibitem{book} M.~Lister, Fundamentals of Operating Systems, 3rd edition (Springer-Verlag, New York, 1984)
%\bibitem{chapter} C.~K.~Clenshaw, K.~Lord, In: B.~K.~P.~Scaife (Ed.), Studies in Numerical Analysis (Academic Press, London and New York, 1974) 95
%\bibitem{arxiv-1} M.~Majewski, K.~Malarz, arXiv:cond-mat/0609635v2 [cond-mat.stat-mech]
%\bibitem{arxiv-2} J.~A.~C.~E.~Solano, arXiv:0707.1343v1 [astro-ph]
%\bibitem{sff-foci2014} A.~Segal, B.~Ford, J.~Feigenbaum, 
%In: J. Crandall and V. Paxson (Eds.), $4^{th}$ Workshop on Free and 
%Open Communications on the Internet, August 18, 2014, San Diego, 
%USA (USENIX, Berkeley, 2014)

\bibitem{sff-foci2014} Bandits, Catching Bandits and Only Bandits:
Privacy-Preserving Intersection Warrants for Lawful Surveillance,
\url{https://drive.google.com/file/d/0BwK1bcoczINtbUhPaFI0Mk1DVk0/view}
(2016)
